\ttitle

### 2015-08-26 Chapters/BodyComp.tex
Body comp - Paper review complete
- All is well.....I think
- Await final comments from Donny

\subsection{Patients}
Patients scheduled to undergo pancreaticoduodenectomy for malignant or benign disease involving the head of the pancreas and periampullary region between August 2008 and October 2010 were included in this study. 
All data were recorded in a prospectively maintained database. 
Data was collected on demographics, preoperative clinico-pathological characteristics including blood tests, body mass index, weight, height and the underlying surgical pathology. 
Detailed breath-by-breath data on a variety of physiological and gas-exchange parameters measured at cardiopulmonary exercise testing were also collected from a prospectively maintained database. 
Cardiopulmonary exercise testing methodolgy is discussed in Section \ref{sec:cpx_method} (p\pageref{sec:cpx_parameters})and a description of the parameters measured at cardiopulmonary exercise testing is provided in Section \ref{sec:cpx_parameters} (p\pageref{sec:cpx_parameters}). A complete dataset for one sample patient is shown in Appendix \ref{AppendixCPETRawData} on p\pageref{AppendixCPETRawData}.

@@

The sequence of steps followed to calculate the area of each tissue compartment is depicted in Fig. \ref{fig:bc_ct_gimp} on p\pageref{fig:bc_ct_gimp}. 
The total cross-sectional area of the abdomen at the level of L3/L4 was calculated by first selecting all the empty space outside the image followed by inverting this selection. 
This is depicted in Fig. \ref{fig:bc_ct_csa}. 
Subcutaneous fat in the image was selected using the Fuzzy Select tool (if necessary by choosing multiple times and removing any unnecessary areas) as depicted in Fig. \ref{fig:bc_ct_sat}. 
The same process was repeated for visceral adipose tissue and skeletal muscle as depicted in Fig. \ref{fig:bc_ct_vat} and Fig. \ref{fig:bc_ct_sm} respectively. 
Every selection was visually confirmed for anatomical accuracy by using the layer selection tool to inspect the selected area as shown in the insets in each of the images.
%CT slices images x 4
\begin{figure}[htbp]
	\centering
	\begin{subfigure}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth]{Figures/bc_ct_csa}
		\caption{Total Cross-sectional Area}
		\label{fig:bc_ct_csa}
	\end{subfigure}
	\begin{subfigure}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth]{Figures/bc_ct_sat}
		\caption{Subcutaneous Adipose Tissue$^*$}
		\label{fig:bc_ct_sat}
	\end{subfigure}
	\hfill
	\begin{subfigure}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth]{Figures/bc_ct_vat}
		\caption{Visceral Adipose Tissue$^*$}
		\label{fig:bc_ct_vat}
	\end{subfigure}
	\begin{subfigure}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth]{Figures/bc_ct_sm}
		\caption{Skeletal Muscle$^*$}
		\label{fig:bc_ct_sm}
	\end{subfigure}

@@

The proportion of skeletal muscle area decreases from 38\% in male patients with normal BMI to 22\% in males who are obese. 
There was a greater decrease in the proportion of skeletal muscle in females with increasing BMI, with skeletal muscle area decreasing from 32\% in females with normal BMI to 14\% in obese females. 
The higher weight in the high BMI patients was due to a disproportionate increase in adipose tissue rather than skeletal muscle. 
Moreover, the distribution of the adipose tissue differed between males and females.
Visceral adipose tissue contributed more to weight in obese males (43\% VAT vs. 35\% SAT) while obese females had a greater proportion of subcutaneous adipose tissue than visceral adipose tissue (18\% VAT vs. 68\% SAT).

@@

Partial correlation analysis was performed to study the relationship between pulmonary function tests and body composition. 
It has been well-established in previous studies that pulmonary function tests are correlated with age and gender and the analysis was therefore adjusted for these two variables. 
Forced Vital Capacity (FVC, litres), Forced Expiratory Volume in 1 second (FEV1, litres) and the ratio FEV1/FVC (Tiffeneau-Pinelli index,\%) were compared against the various components of body composition. 
Both FVC and FEV1 were positively correlated with skeletal muscle area but not with adipose tissue area or total cross-sectional area. 
FEV1/FVC was not correlated with any of the body composition components.

@@

Exercise loads achieved at anaerobic threshold and at peak exercise capacity (at volitional stop rather than maximal exercise) were plotted against skeletal muscle area to create scatter-plots(Fig. \ref{fig:bc_load_vs_sm}, p\pageref{fig:bc_load_vs_sm}. 
Exercise load correlated positively with skeletal muscle area both at anaerobic threshold ($r^{2} = 0.284, p < 0.001$, Fig. \ref{fig:bc_at_load_vs_sm}) and at peak exercise ($r^{2} = 0.350, p < 0.001$, Fig. \ref{fig:bc_pk_load_vs_sm}). 
However, no correlation was identified between exercise loads achieved and adipose tissue area either at anaerobic threshold ($r^{2} = 0.004, p = 0.587$) or peak exercise ($r^{2} = 0.020, p = 0.206$) as shown in Table \ref{table:bc_cpet} on p\pageref{table:bc_cpet}.

@@

Partial correlations between cardiopulmonary exercise parameters at rest, anaerobic threshold and peak exercise versus body composition were adjusted for gender. 
Our own findings (\ref{ch_cpet_jaundice}) and the findings of other authors suggest that age is not related to $\dot{V}_{O_2}$AT or $\dot{V}_{O_2}$Peak and therefore no adjustments were made for age. 
The results of this analysis are shown in Table \ref{table:bc_cpet} (p\pageref{table:bc_cpet}).

@@

Absolute $\dot{V}_{O_2}$ (litres/min) had a strong positive correlation with skeletal muscle area at rest ($\rho = 0.353, p = 0.001$), at anaerobic threshold ($\rho = 0.463, p<0.001$) and at peak exercise ($\rho = 0.375, p = 0.001$). 
However, this correlation was lost after correction of $\dot{V}_{O_2}$ for total body weight and in fact there was a non-significant change in the direction of correlation to the negative.

Absolute $\dot{V}_{O_2}$ (litres/min) had no correlation with total adipose tissue at rest or at peak exercise and only a weak correlation at anaerobic threshold. 
However, corrected for total body weight, there was a strong negative correlation between corrected $\dot{V}_{O_2}$ (ml/kg/min)and total adipose tissue at rest ($\rho = -0.482, p<0.001$), anaerobic threshold ($\rho = -0.400, p<0.001$) and peak exercise ($\rho = -0.374, p = 0.001$).

The loss of the physiological relationship between $\dot{V}_{O_2}$ and skeletal muscle after correcting for total body weight is shown in Fig.\ref{fig:bc_scatter_VO2_skeletal} and the creation of a spurious relationship with total adipose tissue after correction for total body weight is shown in Fig. \ref{fig:bc_scatter_VO2_TAT}.

@@

\subsection{Scaling oxygen consumption to body composition and other factors}
Absolute $\dot{V}_{O_2}$ at the anaerobic threshold was corrected for weight, the square of height, body mass index, skeletal muscle area and estimated lean body mass. Calculation of estimated lean body mass is shown in Section \ref{sec:elbm}.
The resulting values were compared to body composition, height, weight and body mass index using partial correlations controlling for sex (Table \ref{table:bc_at_new_indices} on p\pageref{table:bc_at_new_indices}). 
The results from Table \ref{table:bc_cpet} comparing absolute $\dot{V}_{O_2}$ and corrected $\dot{V}_{O_2}$ at the anaerobic threshold with body composition are reproduced in the first two columns of this table to allow comparison with the new indices.

@@

The loss of the strong positive correlation between absolute $VO_{2}$ (litres/min) and skeletal muscle area after correcting for total body weight further supports the argument that the corrected value for $\dot{V}_{O_2}$ under-reports aerobic capacity in obese patients. 
There was no correlation between pulmonary function tests, tidal volume and minute ventilation and adipose tissue area as well as the slight.
However, a statistically significant, positive correlation was present between adipose tissue and $O_2$Pulse at anaerobic threshold as well as peak exercise but not at rest appear.
These findings suggest that adiposity did not contribute to poor cardiopulmonary exercise performance in this cohort of patients.

@@

Seltzer reported in his 1940 study of 34 subjects, that individuals who were more `lateral' than `linear' had lower oxygen intakes per kilo body weight \parencite{seltzer_body_1940}.
Tanner in his article titled \textit{`Fallacy of per-weight and per-surface area standards, and their relation to spurious correlation'} in the Journal of Applied Physiology in 1947 recognised the dangers of expressing physiological variables as a function of total body mass \parencite{tanner_fallacy_1949}. 
In a detailed analysis comparing $\dot{V}_{O_2}$ and body build, he concluded that \textit{'as the index wt./stature increases, O2/wt. must be expected to decrease purely as a result of the method used for representing the data.'}

@@

In a study aimed at determining the optimal method of expressing $\dot{V}_{O_2}$Max, Maciejczyk and co-workers analysed the differing influence of body fat and lean body mass on aerobic performance in two groups of physically fit men categorised based on their body fat percentage \parencite{maciejczyk_influence_2014}. 
High body mass regardless of composition was correlated negatively with $\dot{V}_{O_2}$ (ml/kg/min) when it was corrected for total body weight penalising otherwise fit men purely based on the proportion of body weight that was contributed by body fat. 
However, when $\dot{V}_{O_2}$ was corrected for lean body mass, they found that the results were similar between the low body fat and high fat body groups. 
They, similar to Goran and co-workers \parencite{goran_total_2000}, recommend that $\dot{V}_{O_2}$ be normalised to lean body mass rather than total body weight.

@@

The term \textit{`spurious correlation'} was first introduced by English mathematician and biometrician, Karl Pearson in 1896. 
He used the term to describe correlations that occurred as a result of using ratios instead of absolute values rather than because of any actual correlations between the variables being studied \parencite{pearson_mathematical_1896}.

Older and co-workers in their pioneering study in 1993 reported that $\dot{V}_{O_2}$AT $<$ 11 ml/kg/min was associated with increased mortality in elderly patients undergoing major abdominal surgery \parencite{older_preoperative_1993}. 
While they did not provide any data on other preoperative or intra-operative factors, they concluded that cardiopulmonary exercise testing was useful in predicting postoperative outcome and that a low $\dot{V}_{O_2}$AT represented cardiac failure. 
This association is repeated in their later work on 548 patients which also showed a clear association between low $\dot{V}_{O_2}$AT (ml/kg/min) and mortality due to cardiovascular causes \parencite{older_cardiopulmonary_1999}. 
The concepts of \textit{'surgical anaerobic threshold'} and \textit{'postoperative cardiac failure'} were introduced later and were described as the \textit{'inability of the heart to meet the demand of postoperative stress.'}\parencite{society_ats/accp_2003}.

Swart and Carlisle als reported that $\dot{V}_{O_2}$AT $<$ 11 ml/kg/min in patients undergoing open colorectal surgery was associated with adverse outcomes \parencite{swart_case-controlled_2012}. 
However, the proportion of females in the low $\dot{V}_{O_2}$AT group was significantly greater than that in the normal $\dot{V}_{O_2}$AT group (24\% vs 51\%). 
The average corrected $\dot{V}_{O_2}$AT in men calculated from the data presented in their paper was 11.02 ml/kg/min while in women it was 9.81 ml/kg/min.

@@

The `obesity paradox' would suggest that, in fact, obese patients are not necessarily at an increased risk of postoperative complications. 
Several authors have reported that obesity is not a risk factor for major complications after pancreaticoduodenectomy \parencite{khan_does_2010, tsai_impact_2010, balentine_obesity_2011}. 
In a large study of 118,707 patients undergoing non-bariatric general surgery, the authors reported that the risk of death was `paradoxically' low in the overweight and obese group of patients \parencite{mullen_obesity_2009}. 
The results of the present study show that $\dot{V}_{O_2}$ as is currently reported for clinical use will also be low in this very same cohort of patients. 
This obesity paradox is particularly apparent in patients with heart failure where in spite of a low $\dot{V}_{O_2}$ (corrected for total body weight), obese patients have better survival rates. 
Horwich and co-workers reported in a study of 2331 patients that body mass index was associated with a low $\dot{V}_{O_2}$Peak (ml/kg/min) independent of all other factors including age, diabetes, cardiac disease, New York Heart Association Class of cardiac failure and race \parencite{horwich_relationship_2009}.

@@

However, the results presented in this study demonstrate that the success of such prehabilitation programs must not be determined solely by $\dot{V}_{O_2}$ corrected for total body weight. 
Instead, improvement in the absolute values of $\dot{V}_{O_2}$AT and $\dot{V}_{O_2}$Peak in conjunction with improvement in other parameters that are not affected by body composition such as $O^2$Pulse, tidal volume \parencite{jones_effects_2007} or maximal exercise load \parencite{kim_responsive_2009} may provide more reliable evidence of improvement in aerobic capacity.

The combination of nutritional assessment and advice, home-based exercise programs and weight loss may help improve aerobic capacity and eventually postoperative outcomes. 
Such preoperative interventions may also be associated with improvements in body composition with increase in skeletal muscle mass and reduction in adipose tissue.
This may result in apparent improvements in cardiopulmonary exercise test parameters that are scaled using total body weight.
Further studies are required to validate the findings presented here as well as to identify optimal scaling methods for cardiopulmonary exercise test parameters. 
This will improve the clinical utility of cardiopulmonary exercise testing in the preoperative risk assessment as well as optimisation of patients undergoing major surgery.

>>>>

\subsection{Patients}
Patients scheduled to undergo pancreaticoduodenectomy for malignant or benign disease involving the head of the pancreas and periampullary region between August 2008 and October 2010 were included in this study. 
All data were recorded in a prospectively maintained database. 
Data was collected on demographics, preoperative clinico-pathological characteristics including blood tests, body mass index, weight, height and the underlying surgical pathology. 
Detailed breath-by-breath data on a variety of physiological and gas-exchange parameters measured at cardiopulmonary exercise testing were also collected from a prospectively maintained database. 
Cardiopulmonary exercise testing methodolgy is discussed in Section \ref{sec:cpx_method} (page \pageref{sec:cpx_parameters})and a description of the parameters measured at cardiopulmonary exercise testing is provided in Section \ref{sec:cpx_parameters} (page \pageref{sec:cpx_parameters}). A complete dataset for one sample patient is shown in Appendix \ref{AppendixCPETRawData} on page \pageref{AppendixCPETRawData}.

@@

The sequence of steps followed to calculate the area of each tissue compartment is depicted in Fig. \ref{fig:bc_ct_gimp} on page \pageref{fig:bc_ct_gimp}. 
The total cross-sectional area of the abdomen at the level of L3/L4 was calculated by first selecting all the empty space outside the image followed by inverting this selection. 
This is depicted in Fig. \ref{fig:bc_ct_csa}. 
Subcutaneous fat in the image was selected using the Fuzzy Select tool (if necessary by choosing multiple times and removing any unnecessary areas) as depicted in Fig. \ref{fig:bc_ct_sat}. 
The same process was repeated for visceral adipose tissue and skeletal muscle as depicted in Fig. \ref{fig:bc_ct_vat} and Fig. \ref{fig:bc_ct_sm} respectively. 
Every selection was visually confirmed for anatomical accuracy by using the layer selection tool to inspect the selected area as shown in the insets in each of the images.
%CT slices images x 4
\begin{figure}[htbp]
	\centering
	\begin{subfigure}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth]{Figures/bc_ct_csa}
		\caption{Total Cross-sectional Area}
		\label{fig:bc_ct_csa}
	\end{subfigure}
	\begin{subfigure}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth]{Figures/bc_ct_sat}
		\caption{Subcutaneous Adipose Tissue$^*$}
		\label{fig:bc_ct_sat}
	\end{subfigure}
	\hfill
	\begin{subfigure}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth]{Figures/bc_ct_vat}
		\caption{Visceral Adipose Tissue$^*$}
		\label{fig:bc_ct_vat}
	\end{subfigure}
	\begin{subfigure}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth]{Figures/bc_ct_sm}
		\caption{Skeletal Muscle$^*$}
		\label{fig:bc_ct_sm}
	\end{subfigure}

@@

The proportion of skeletal muscle area decreased from 38\% in male patients with normal BMI to 22\% in obese males. 
There was a greater decrease in the proportion of skeletal muscle in females with increasing BMI, with skeletal muscle area decreasing from 32\% in females with normal BMI to 14\% in obese females. 
The higher weight in the overweight/obese patients was due to a disproportionate increase in adipose tissue rather than skeletal muscle. 
Moreover, the distribution of the adipose tissue differed between males and females.
Visceral adipose tissue contributed more to weight in obese males (43\% VAT vs. 35\% SAT) while obese females had a greater proportion of subcutaneous adipose tissue than visceral adipose tissue (18\% VAT vs. 68\% SAT).

@@

Partial correlation analysis was performed to study the relationship between pulmonary function tests and body composition. 
It has been well-established in previous studies that pulmonary function tests are correlated with age and sex and the analysis was therefore adjusted for these two variables. 
Forced Vital Capacity (FVC, litres), Forced Expiratory Volume in 1 second (FEV1, litres) and the ratio FEV1/FVC (Tiffeneau-Pinelli index,\%) were compared against the various components of body composition. 
Both FVC and FEV1 were positively correlated with skeletal muscle but not with adipose tissue area. 
FEV1/FVC was not associated with any of the body composition components.

@@

Exercise loads achieved at anaerobic threshold and at peak exercise capacity were plotted against skeletal muscle area to create scatter-plots(Fig. \ref{fig:bc_load_vs_sm} on page \pageref{fig:bc_load_vs_sm}).  
Exercise load correlated positively with skeletal muscle area both at anaerobic threshold ($\rho^2 = 0.284, p < 0.001$, Fig. \ref{fig:bc_at_load_vs_sm}) and at peak exercise ($\rho^2 = 0.350, p < 0.001$, Fig. \ref{fig:bc_pk_load_vs_sm}). 
However, no correlation was identified between exercise loads achieved and adipose tissue area either at anaerobic threshold ($\rho^2 = 0.004, p = 0.587$) or peak exercise ($\rho^2 = 0.020, p = 0.206$) as shown in Table \ref{table:bc_cpet} on page \pageref{table:bc_cpet}.

@@

Partial correlations between cardiopulmonary exercise parameters at rest, anaerobic threshold and peak exercise versus body composition were adjusted for sex. 
Our own findings (Tables \ref{table:cpet_oj_at_regression} and \ref{table:cpet_oj_peak_regression} on pages \pageref{table:cpet_oj_at_regression}, \pageref{table:cpet_oj_peak_regression}) and the findings of other authors suggest that age is not related to $\dot{V}_{O_2}$AT or $\dot{V}_{O_2}$Peak and therefore no adjustments were made for age. 
The results of this analysis are shown in Table \ref{table:bc_cpet} (page \pageref{table:bc_cpet}).

@@

Absolute $\dot{V}_{O_2}$ (litres/min) had a strong positive correlation with skeletal muscle area at rest ($\rho = 0.353, p = 0.001$), at anaerobic threshold ($\rho = 0.463, p<0.001$) and at peak exercise ($\rho = 0.375, p = 0.001$). 
However, this correlation was lost after correction of $\dot{V}_{O_2}$ for total body weight and there was a non-significant change in the direction of correlation to the negative.

Absolute $\dot{V}_{O_2}$ (litres/min) had no correlation with total adipose tissue at rest or at peak exercise and only a weak correlation at anaerobic threshold. 
However, when corrected for total body weight, there was a strong negative correlation between corrected $\dot{V}_{O_2}$ (ml/kg/min)and total adipose tissue at rest ($\rho = -0.482, p<0.001$), anaerobic threshold ($\rho = -0.400, p<0.001$) and peak exercise ($\rho = -0.374, p = 0.001$).

The loss of physiological relationship between $\dot{V}_{O_2}$ and skeletal muscle after correcting for total body weight is shown in Fig.\ref{fig:bc_scatter_VO2_skeletal} and the creation of a spurious relationship with total adipose tissue after correction for total body weight is shown in Fig. \ref{fig:bc_scatter_VO2_TAT}.

@@

\subsection{Scaling oxygen consumption to body composition and other factors}
Absolute $\dot{V}_{O_2}$ at the anaerobic threshold was corrected for weight, the square of height, body mass index, skeletal muscle area and estimated lean body mass. Calculation of estimated lean body mass is shown in Section \ref{sec:elbm}.
The resulting values were compared to body composition, height, weight and body mass index using partial correlations controlling for sex (Table \ref{table:bc_at_new_indices} on page \pageref{table:bc_at_new_indices}). 
The results from Table \ref{table:bc_cpet} comparing absolute $\dot{V}_{O_2}$ and corrected $\dot{V}_{O_2}$ at the anaerobic threshold with body composition are reproduced in the first two columns of this table to allow comparison with the new indices.

@@

The loss of the strong positive correlation between absolute $VO_{2}$ (litres/min) and skeletal muscle area after correcting for total body weight further supports the argument that the corrected value for $\dot{V}_{O_2}$ under-reports aerobic capacity in obese patients. 
There was no correlation between pulmonary function tests, tidal volume and minute ventilation and adipose tissue area. 
However, a statistically significant, positive correlation was present between adipose tissue and $O_2$Pulse at anaerobic threshold as well as peak exercise but not at rest.
These findings suggest that adiposity did not contribute to poor cardiopulmonary exercise performance in this cohort of patients.

@@

Seltzer reported in his 1940 study of 34 subjects that individuals who were more `lateral' than `linear' had lower oxygen intakes per kilo body weight \parencite{seltzer_body_1940}.
Tanner in his article titled \textit{`Fallacy of per-weight and per-surface area standards, and their relation to spurious correlation'} in the Journal of Applied Physiology in 1947 recognised the dangers of expressing physiological variables as a function of total body mass \parencite{tanner_fallacy_1949}. 
In a detailed analysis comparing $\dot{V}_{O_2}$ and body build, he concluded that \textit{'as the index wt./stature increases, O2/wt. must be expected to decrease purely as a result of the method used for representing the data.'}

@@

In a study aimed at determining the optimal method of expressing $\dot{V}_{O_2}$Max, Maciejczyk and co-workers analysed the differing influence of body fat and lean body mass on aerobic performance in two groups of physically fit men categorised based on their body fat percentage \parencite{maciejczyk_influence_2014}. 
High body mass regardless of composition was correlated negatively with $\dot{V}_{O_2}$ (ml/kg/min) when it was corrected for total body weight.
This penalised otherwise fit men purely based on the proportion of body weight that was contributed by body fat. 
However, when $\dot{V}_{O_2}$ was corrected for lean body mass, they found that the results were similar between the low body fat and high fat body groups. 
They, similar to Goran and co-workers \parencite{goran_total_2000}, recommend that $\dot{V}_{O_2}$ be normalised to lean body mass rather than total body weight.

@@

The term \textit{`spurious correlation'} was first introduced by English mathematician and biometrician, Karl Pearson, in 1896. 
He used the term to describe correlations that occurred as a result of using ratios instead of absolute values rather than because of any actual correlations between the variables being studied \parencite{pearson_mathematical_1896}.

Older and co-workers in their pioneering study in 1993 reported that $\dot{V}_{O_2}$AT $<$ 11 ml/kg/min was associated with increased mortality in elderly patients undergoing major abdominal surgery \parencite{older_preoperative_1993}. 
While they did not provide any data on other preoperative or intra-operative factors, they concluded that cardiopulmonary exercise testing was useful in predicting postoperative outcome and that a low $\dot{V}_{O_2}$AT represented cardiac failure. 
This assertion is repeated in their later work on 548 patients which also showed a clear association between low $\dot{V}_{O_2}$AT (ml/kg/min) and mortality due to cardiovascular causes \parencite{older_cardiopulmonary_1999}. 
The concepts of \textit{'surgical anaerobic threshold'} and \textit{'postoperative cardiac failure'} were introduced later and were described as the \textit{'inability of the heart to meet the demand of postoperative stress.'}\parencite{society_ats/accp_2003}.

Swart and Carlisle als0 reported that $\dot{V}_{O_2}$AT $<$ 11 ml/kg/min in patients undergoing open colorectal surgery was associated with adverse outcomes \parencite{swart_case-controlled_2012}. 
However, the proportion of females in the low $\dot{V}_{O_2}$AT group was significantly greater than that in the normal $\dot{V}_{O_2}$AT group (24\% vs 51\%). 
The average corrected $\dot{V}_{O_2}$AT in men calculated from the data presented in their paper was 11.02 ml/kg/min while in women it was 9.81 ml/kg/min.

@@

The `obesity paradox' would suggest that, in fact, obese patients are not necessarily at an increased risk of postoperative complications. 
Several authors have reported that obesity was not a risk factor for major complications after pancreaticoduodenectomy \parencite{khan_does_2010, tsai_impact_2010, balentine_obesity_2011}. 
In a large study of 118,707 patients undergoing non-bariatric general surgery, the authors reported that the risk of death was `paradoxically' low in the overweight and obese group of patients \parencite{mullen_obesity_2009}. 
The results of the present study show that $\dot{V}_{O_2}$ as is currently reported for clinical use will also be low in this very same cohort of patients. 
This obesity paradox is particularly apparent in patients with heart failure where in spite of a low $\dot{V}_{O_2}$ (corrected for total body weight), obese patients have better survival rates. 
Horwich and co-workers reported in a study of 2331 patients that body mass index was associated with a low $\dot{V}_{O_2}$Peak (ml/kg/min) independent of all other factors including age, diabetes, cardiac disease, New York Heart Association Class of cardiac failure and race \parencite{horwich_relationship_2009}.

@@

However, the results presented in this study demonstrate that the success of such prehabilitation programs must not be determined solely by $\dot{V}_{O_2}$ corrected for total body weight. 
Instead, improvement in the absolute values of $\dot{V}_{O_2}$AT and $\dot{V}_{O_2}$Peak in conjunction with improvement in other parameters that are not affected by body composition such as $O_2$Pulse, tidal volume \parencite{jones_effects_2007} or maximal exercise load \parencite{kim_responsive_2009} may provide more reliable evidence of improvement in aerobic capacity.

The combination of nutritional assessment and advice, home-based exercise programs and weight loss may help improve aerobic capacity and eventually postoperative outcomes. 
Such preoperative interventions may also be associated with improvements in body composition with increase in skeletal muscle mass and reduction in adipose tissue.
This may result in apparent improvements in cardiopulmonary exercise test parameters that are scaled using total body weight as well as improvements in true aerobic fitness.
Further studies are required to validate the findings presented here as well as to identify optimal scaling methods for cardiopulmonary exercise test parameters. 
This will improve the clinical utility of cardiopulmonary exercise testing in the preoperative risk assessment as well as optimisation of patients undergoing major surgery.
